Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-23 paper.tex
Emphasize early ray termination in abstract (ref #18)

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Unfortunately the traditional method for rendering intersecting volumes using
hardware acceleration requires a large amount of geometry to be created every
frame.  In the simple case where two axis-aligned volumes intersect, it is shown
that Boolean operations can be used so that the camera may move without
regenerating any geometry.  Furthermore, samples that do not contribute to the
final image may be completely avoided.  The two variations presented herein
achieve higher frame rates than the traditional slicing method.
\end{abstract}

>>>>

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Unfortunately the traditional method for rendering intersecting volumes using
hardware acceleration requires a large amount of geometry to be created every
frame.  In the simple case where two axis-aligned volumes intersect, it is shown
that Boolean operations can be used so that the camera may move without
regenerating any geometry.  Originally the two variations presented herein
still achieved similar frame rates.  However, after implementing early ray
termination, they have proven faster for typical data sets.
\end{abstract}
